The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-08 rational.tex
diagram1 for negatives
diagrams
sat

FIGURE

@@

%%%%%%%%%%%%%%%%%%%%%
\subsection{Multiplicative Duality in {{langRev}} }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Advanced Programming Examples}
\label{sec:prog}

%%%%%%%%%%%%%%%%%%%
\subsection{SAT solver}
\label{sec:sat-solver}

@@

>>>>

\begin{center}
  \includegraphics{diagrams/algebra1.pdf}
\end{center}

\roshan{I chose to draw the igure with b instead of a, since b is what
  we use for the types. Should this be a? Also I chose to make the
  swap and 0 wires, explicit.Is this what you intended? }

@@

\begin{center}
  \includegraphics{diagrams/algebra2.pdf}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Multiplicative Duality in {{langRev}} }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SAT Solver in {{langRevEE}} }
\label{sec:prog}

%%%%%%%%%%%%%%%%%%%
% \subsection{SAT solver}
\label{sec:sat-solver}

@@

\roshan{Explain how the dotted part is implemented.}

Let us call this construction which maps inputs, heap and control
wires to input, heap and control wires as {{sat_f}}. The required
contraint solver is then constructed as shown:

\begin{center}
\scalebox{1.5}{
  \includegraphics{diagrams/sat3.pdf}
}
\end{center}
